Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

There could even be an incidence of the intention to perform a certain behaviour and the actual performance of that behaviour, which could lead to look into skills, abilities and willpower. It is almost like "individuals would be predisposed to entrepreneurial intentions based upon a combination of both personal and contextual factors" ????? Boyd and Vosikis MAIN BIB ????? but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality.

>>>>

There could even be an incidence of the intention to perform a certain behaviour on the actual performance of that behaviour, which could lead to look into skills, abilities and willpower. It is almost like "individuals would be predisposed to entrepreneurial intentions based upon a combination of both personal and contextual factors" ????? Boyd and Vosikis MAIN BIB ????? but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality for "self-efficacy will moderate the relationship between the development of entrepreneurial intentions and the likelihood that these intentions will result in entrepreneurial actions or behaviour".
